\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Shorten a bit.

The trusted value relation includes everything that the untrusted value relation contains and a few extra things.
The trusted code uses the return seals and the closure seals in its program, and it does so in a responsible way which is why sets of seals with trusted return seals and closure seals are in the trusted value relation.
In order for trusted code to even execute, it needs to use an executable memory capability for the trusted code, so such capabilities are in the untrusted value relation.\footnote{Note that code capabilities for trusted code is not allowed in the untrusted value relation as it could be used to read return seals that are not in the untrusted value relation.}

@@

\subsubsection{Fundamental theorem}
With the logical relation defined, we state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr), ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W) \qedhere
  \]
\end{lemma}
Roughly speaking, the FTLR says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ entails, and for trusted code the semantic reasonability condition must also be satisfied.
The proof of the FTLR is done by a nested induction where each instruction that could be executed is considered.
While the lemma is not directly used in the proof sketch we present in Section~\ref{subsec:proof-sketch}, it is detrimental to the proofs of the lemmas in that section.

>>>>

The trusted value relation includes everything that the untrusted value relation contains and a few extra things.
Trusted code uses the return seals and the closure seals (in a responsible way), and therefore sets of seals with trusted return seals and closure seals are in the trusted value relation.
In order for trusted code to even execute, it needs to use an executable memory capability for the trusted code, so such capabilities are in the untrusted value relation.\footnote{Note that code capabilities for trusted code is not allowed in the untrusted value relation as it could be used to read return seals that are not in the untrusted value relation.}

@@

\subsubsection{Fundamental theorem}
With the logical relation defined, we state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr), ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W) \qedhere
  \]
\end{lemma}
Roughly speaking, the FTLR says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ entails, and for trusted code the semantic reasonability condition must also be satisfied.
The proof of the FTLR is done by a nested induction where each instruction that could be executed is considered.
The lemma is not directly used in the proof sketch we present in Section~\ref{subsec:proof-sketch}, but it is crucial to the proofs of the lemmas in that section.
